upwell_IDX

### 2019-08-21 upwell_IDX.Rmd
Added a filter

# Calculate quantiles of upwelling index
SACTN_upwell_quantiles <- SACTN_upwell %>% 
  group_by(site) %>% 
  summarize(quant_10 = quantile(ui.saws, probs = 0.10, na.rm = TRUE),
            quant_25 = quantile(ui.saws, probs = 0.25, na.rm = TRUE),
            quant_50 = quantile(ui.saws, probs = 0.50, na.rm = TRUE),
            quant_75 = quantile(ui.saws, probs = 0.75, na.rm = TRUE),
            quant_90 = quantile(ui.saws, probs = 0.90, na.rm = TRUE))

>>>>

# Calculate quantiles of upwelling index
SACTN_upwell_quantiles <- SACTN_upwell %>%
  filter(ui.saws >= 0) %>% 
  group_by(site) %>% 
  summarize(quant_10 = quantile(ui.saws, probs = 0.10, na.rm = TRUE),
            quant_25 = quantile(ui.saws, probs = 0.25, na.rm = TRUE),
            quant_50 = quantile(ui.saws, probs = 0.50, na.rm = TRUE),
            quant_75 = quantile(ui.saws, probs = 0.75, na.rm = TRUE),
            quant_90 = quantile(ui.saws, probs = 0.90, na.rm = TRUE))
